Exposure Consequences - Statistics and Figures

### 2018-02-02 ManuscriptMaterials.Rmd
expanded conclusions, added one LME for classic localization that focusses on movement type (ignores hand angle)

In the exposure group there is no effect of movement type, but we see one here. This could be because the effect of movement type is much larger in the classic group. This would predict an interaction between group and movement type, but this is not even a trend (p=.133). Hence we tested for an effect of movement type in the classic group:

@@

```{r fig.width=7.5, fig.height=4}
correlations <- correlateNoCursorsLocalization()
```

@@

So this doesn't work either.

>>>>

In the exposure group there is no effect of movement type, but we see one here. This could be because the effect of movement type is much larger in the classic group. This would predict an interaction between group and movement type, but this is not even a trend (p=.133).

What if we don't care about hand angle:

```{r loc_groups_movementtype}
groupLocalization(model='movementtype',remove15=TRUE)
```

Now there is a trend towards significance for the interaction between training group and movement type. That is closer to what we would expect.

Let's see if the classic group shows an effect of movement type (with the current preprocessing procedures):

@@

```{r scattergrams, fig.width=7.5, fig.height=4}
correlations <- correlateNoCursorsLocalization()
```

@@

But no.

# Conclusions

What can we conclude? Here is an initial list of what we might conclude.

1. Exposure training leads to robust reach aftereffects that are similar to those after classic training, although they seem to have a more pronouced generalization curve. This means that evoking propceptive recalibration with visual-proprioceptive discrepancies leads to motor changes. In other words: proprioception informs movement plans.

2. Exposure training leads to shifts in localization, that are not very different between active and passive localization. Since both active and passive movements access recalibrated proprioception, while active localization also accesses updated predictions, this indicates that hand localization is makes very good use of proprioception.

    1. Additionally, since predictions should not be updated in exposure training, but active localization might be evoking a slightly larger shift, this indicates a non-Bayesian process of combining predictions and perceptions in this case.

    2. After classic training (2016 paper) there was an effect of movement type, which indicates that with a training regime that allows updates of predicted sensory consequences, these updates do indeed also affect hand localization.

    3. Within the workspace however, there is no interaction between movement type and training group. Perhaps there is a small update of predicted proprioceptive consequences, that we can't parcel out. A more computational approach would be needed to see if this can explain the pattern of results here.

3. Recalibrated proprioception can reliably predict reach aftereffects, but only after **exposure** training and for _active localization_. This means that recalibrated proprioception indeed leads to motor changes.

    1. There is also a trend towards significance for _passive localization_ to predict reach aftereffects after **classic training**. Perhaps active localization is more similar to no-cursor reaches after exposure training, as both of these can only use recalibrated proprioception as well as updated predictions of proprioceptive consequences. This does not explain the trend towards significance for predicting classic reach aftereffects with passive localization. However, a step-wise multiple regression favours an intercept model for classic reach aftereffects, and a model that mostly relies on active localization for exposure reach aftereffects. So perhaps not too much should be read into the trend towards significance in the correlation. On the other hand, the exposure group had twice as much data, so that the estimated recalibration would be more reliable within each participant. Perhaps with higher quality estimates of proprioceptive recalibration those would be able to predict part of the reach aftereffects even after classic training.
